\forestclaw: Hybrid forest-of-octrees AMR for hyperbolic conservation laws

### 2013-03-18 docs/parco13/abstract.tex
Add text and figure for results section

* sphere results\\
* swirl example

To come...

Parallelization is not completed yet but envisioned for the final version of
the paper.

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=.4\columnwidth]{quadtree}
\hspace{.05\columnwidth}
\includegraphics[width=.4\columnwidth]{sphere_plot167}
\end{center}
\caption{Numerical results for solving the advection equation.  Left:  Unit
square (single quadtree) with a twisting velocity field.  Right: Spherical ball
with a rotational velocity field constructed from two mapped quadtrees.  In
both cases the concentration is color-coded with a sharp gradient shown in red.
The adaptive mesh refinement follows the location of the gradient (the patches
are not shown where they become too fine for display).  Here we use $m = 8$
cells per \clawpack patch.}
\label{results2d}
\end{figure}

The results in this section are preliminary and will be extended in the final
version.  We have so far exercised \forestclaw for two 2D manifolds, namely the
unit square and a sphere composed of two mapped squares.  On both we solve the
advection equation with a given velocity field.  We advect a concentration
field with a sharp gradient which we track dynamically with adaptive mesh
refinement.  We observe that the refinement follows the front and allows for an
accurate representation of its location over time; see Figure~\ref{results2d}.

\pforest is parallelized with MPI and well tested on large supercomputers, both
in 2D and 3D.  Parallelization of \forestclaw is not completed yet but
envisioned for the final version of the paper.
